RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-02-14 paper.tex
bit of related work

\section{Architecture}

>>>>

Kandel's interview study points out the typical ``explore'',
``model'', ``report'' cycle~\cite{Kandel:2012:EDA}. RCloud seeks to
reduce the impedance mismatch.

Heer and Agarwala identify a large number of design considerations for
collaborative visual analytics~\cite{Heer:2008:DCF}. \emph{Starring},
the system for signaling interest in notebooks, described in
Section~\ref{sec:starring}, addresses social-psychological incentives,
recommendation, and voting and ranking. RCloud's integrated deployment
mechanism, described in Section~\ref{sec:deployment}, adresses cost of
integration, content export, presentation and view sharing. Notebooks,
and the integrated version control system for them, described in
Section~\ref{sec:notebooks}, addresses modularity and granularity, and
artifact histories.

\section{System Architecture}

\section{System Design}

\subsection{Notebooks\label{sec:notebooks}}

\subsection{Reputation and Interest: starring\label{sec:starring}}

\subsection{Deployment of notebooks\label{sec:deployment}}
